\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
fix another typo

In addition \fs has already undergone some user testing. This includes
analytic tests of the $R$-symmetric low-energy model (MRSSM) and
alternative E6 inspired SUSY scenarios.  The users who have helped us
with this are thanked in the acknowledgements.

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Philip Diessner
for testing and identifying several bugs in FlexibleSUSY and in SARAH,
in work on the MRSSM; Ulrik Günther for compilation tests on Mac OS X
and Dylan Harries for spotting a bug in the configuration script.
%
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.

>>>>

In addition \fs has already undergone some user testing. This includes
analytic tests of the $R$-symmetric low-energy model (MRSSM) and
alternative $E_6$-inspired SUSY scenarios.  The users who have helped us
with this are thanked in the acknowledgements.

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Philip Diessner
for testing and identifying several bugs in \fs and in SARAH,
in work on the MRSSM; Ulrik Günther for compilation tests on Mac OS X
and Dylan Harries for spotting a bug in the configuration script.
%
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.
